\newpage
\section{MetaDoc Server API}
\label{sec:server_api}

The MetaDoc server implements a REST-like \gls{api}, however, there are certain
differences from REST noted in section \ref{sec:diff_from_rest}.

When the client performs a GET request on an available URL, the server should
return an \gls{xml} document, or a HTTP status code refering to an error.  The
\gls{xml} document should follow the MetaDoc \gls{dtd} \cite{metadoc_dtd}. Each
URL only returns data from the requested data type. This means that a request
to \textbf{baseurl/allocations/} will return an MetaDoc \gls{xml} document
containing only an \texttt{<allocations>} directly on the \texttt{<MetaDoc>}
root, with \texttt{<all\_entry>} tags as children of \texttt{<allocations>}.
The client should disregard any information outside \texttt{<allocations>} when
connecting to \textbf{baseurl/allocations/}. 

In order to send data to the server, the client performs a POST request, with
the POST data variable \texttt{metadoc} containing a MetaDoc \gls{xml}
document. The server will only accept data from the data type specified in the
URL, and will disregard any other information. This means that a POST to
\textbf{baseurl/events/} should be a MetaDoc \gls{xml} document containing a
\texttt{<events>} tag directly on the \texttt{<MetaDoc>} root, with any number
of \texttt{<resourceUp>} and \texttt{<resourceDown>} tags as children of
\texttt{<events>}. 

When this data is sent to the server, the server should return a MetaDoc
\gls{xml} document containing a \texttt{<receipts>} tag, with a
\texttt{<r\_entry>} tag for each element recieved that has an
\textbf{id}-attribute. This allows for a very fine grained error reporting.

\subsection{Available URLs}

\begin{description}
    \item[/allocations/] Retrieves a list of allocations/quotas relevant
        to the client
    \item[/users/] Retrieves a list of users for the client
    \item[/projects/] Retrieves a list of projects relevant to the
        client
    \item[/config/] Sends system configuration to server
    \item[/events/] Sends site events to the server
    \item[/software/] Sends system software to server
\end{description}

\subsection{Authentication}
\label{sec:authentication}
The server uses X.509 certificates to authenticate the client. In order for the
site to be authenticated properly, the server must be aware of the client's
certificate prior to the request, and the correct owner of the certificate must
be saved on the server. This \textit{must} be the same as the value for
\texttt{site\_name} set in the MetaDoc configuration (see section
\ref{sec:metadoc_conf}).

\subsection{Differences from REST}
\label{sec:diff_from_rest}

There are certain differences in the \gls{api} compared to the REST
specification. The MetaDoc Server \gls{api} makes use of HTTP POST where HTTP
PUT should be used in accordance with REST. This is due to limitations in
standard Python libraries.

Because the MetaDoc Server does not give the client access to delete or replace
data on the server, this does not create problems for the Server \gls{api}. %FIXME

\subsection{Server HTTP responses}

The server makes use of HTTP status codes to identify what error has occoured
if the server is unable or unwilling to process the request from the server.
Table \ref{tbl:http_status_codes} contains a list of status codes the server
returns, and why these status codes occour. 

\begin{table}[h!]
    \centering
    \caption{List of HTTP status codes used by the MetaDoc Server}
    \begin{tabular}{|l|l|p{7cm}|}
        \hline
        \textbf{Code} & \textbf{Official name} & \textbf{MAPI-Reason} \\
        \hline
        200 & 200 OK & The server has processed the request and should return
        an \gls{xml} document. \\
        \hline
        400 & 400 Bad Data & The data excepted from the client was not sent, or
        the \gls{xml} document did not validate against the \gls{dtd} or was
        malformed \gls{xml}. \\
        \hline
        403 & 403 Forbidden & The client certificate was not recognized as an
        authorative source for the site given in the \gls{xml} document. \\
        \hline
        404 & 404 Not found & The URL the client is attempting to access is not
        available on the server. Check host in \texttt{metadoc.conf}. If host
        is correct, make sure client and server uses same version. See section
        \ref{sec:version} for more information on version differences. \\ 
        \hline
        500 & 500 Server Error & The server failed to process the request. This
        does not include errors that return a receipt. \\
        \hline
        501 & 501 Not Implemented & The request method is not implemented for
        this URL. This will happen if the client attempts to use a request
        method that is not implemented for this URL, such as using the POST
        request method against an URL that only supports GET. \\
        \hline
    \end{tabular}
    \label{tbl:http_status_codes}
\end{table}
